---
output: github_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`podr` is a very simple package containing two functions for reading and cleaning data from a podcast feed. 

## Installation
```{r eval=FALSE}
devtools::install_github("erramirez/podr")
```

## Key Functions

`podr` is primarily composed of two functions:

1. The first function, `readpod`, will extract relevant information from a podcast feed according to the information available within the **item** node. Additionally, it will read and append the podcast title according to what is present in **channel/title**.
2. The second function, `cleapod`, will read a data frame created with `readpod` and reduce to a tibble with four variables:
    + podtitle: the title of the podcast
    + title: the episdoe title
    + date: the date the episode was published
    + showlength: the duration of the podcast in seconds
    
`cleanpod` is primarily used to clean up the date and duration information in a podcast feed in order to make it computable. 

## Usage  
Let't say you were really interested in learning how much time you spent listening to your favorite podcast, _Jordan, Jesse Go!_, in 2017. 

First we would use `readpod` to read the podcast feed. 

```{r}
library(podr)

jjgo <- readpod("http://thornmorris.libsyn.com/rss")

jjgo
```

We can then use `cleanpod` to clean up the podcast data to something usable to answer our question. 

```{r}
jjgoclean <- cleanpod(jjgo)

jjgoclean
```

Now that we have a cleaned data set that contains all the relevant information we can use a few simple tidy tools. 

```{r message=FALSE}

library(tidyverse)
library(lubridate)

jjgoclean2k17 <- jjgoclean %>% 
  filter(date > "2016-12-31" & date < "2018-01-01")

#find the total duration of Jordan, Jesse GO! in seconds
sum(jjgoclean2k17$showlength)

#find the total as a period 
seconds_to_period(sum(jjgoclean2k17$showlength))

```

So there you have it. You can use `podr` to find out _Jordan, Jesse GO!_ put out **2d 18H 52M 7S** of hilarious shows in 2017. 

## Note
Please feel free to share issues, notes, and ideas. This is my first public R package and I'd love to learn from you. 

_made with RStudio and_ ❤️ _in_ ☀️ _Los Angeles_




