---
title: "README"
date: "1/28/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`podr` is a very simple package containing two function for reading and cleaning data from a podcast feed. 

## Installation
```{r eval=FALSE}
devtools::install_github("erramirez/podr")
```

`podr` will load two packages: `xml2` and `tidyverse`.

## Key Functions

`podr` is primarily composed of two functions:
1. `readpod` will extract relevant information from a podcast feed according to the information available within the <item> node. Additionally, it will read and append the podcast title according to what is present in <channel><title>.
2. `cleapod` will read a data frame created with `readpod` and reduce to a tibble with four variables:
  + podtitle: the title of the podcast
  + title: the episdoe title
  + date: the date the episode was published
  + showlength: the duration of the podcast in seconds
`cleanpod` is primarily used to clean up the date and duration information in a podcast feed in order to make it computable. 

## Usage  
Let't say you were really interested in learning how much time you spent listening to your favorite podcat, **Jordan, Jesse Go!**, in 2017. 

First we would use `readpod` to read the podcast feed. 

```{r}
library(podr)

jjgo <- readpod("http://thornmorris.libsyn.com/rss")

jjgo
```

We can then use `cleanpod` to clean up the podcast data to something usable to answer our question. 

```{r}
jjgoclean <- cleanpod(jjgo)

jjgoclean
```

Now that we have a cleaned data set that contains all the relevant information we can use a few simple tidy tools. 

```{r}

jjgoclean %>% 
  filter(date > "2016-12-31" & date < "2018-01-01") %>% 
  second_to_period(sum(showlength))

```


